---
title: "Revision part II (kantar)"
author: "Erik"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
require("tidyverse")
require("haven")
require("forcats")
require("stargazer")
require("ggplot2")
require("multcomp")
require("multiwayvcov")
```

# Reading in data.
I have saved data from `reading_kantar_files.Rmd` into memory.
```{r, message=FALSE, warning=FALSE}
treatmentsv = c("Base (w)", "Forced Choice (w)", "Nominal Choice (w)", 
                "Base (nw)", "Forced Choice (nw)", "Nominal Choice (nw)",
                "Forced Choice strong", "Forced Choice very strong")
treatmentsv_short = c("Base", "Forced Choice", "Nominal Choice")
df_k <- read_csv("data/bl_kantar.csv", na=c("","NA","NaN"), guess_max=10000) %>% 
  mutate(treatment = factor(treatment, levels=treatmentsv),
         treatment_kantar = factor(treatment_kantar),
         treatmentgroup = factor(treatmentgroup, levels=treatmentsv_short),
         treatmentgroup8 = fct_recode(treatment,
                                      "Base" = "Base (w)",
                                      "Base" = "Base (nw)",
                                      "Nominal Choice" = "Nominal Choice (w)",
                                      "Nominal Choice" = "Nominal Choice (nw)",
                                      "Forced Choice" = "Forced Choice (w)",
                                      "Forced Choice" = "Forced Choice (nw)",
                                      "Forced Choice" = "Forced Choice strong",
                                      "Forced Choice" = "Forced Choice very strong"),
         gender = factor(gender),
         education = factor(education),
         indincome = factor(indincome),
         work_temp = fct_relevel(as.factor(workp), c("TRUE", "FALSE")),
         work = fct_recode(work_temp, 
                           "Work" = "TRUE", 
                           "No Work"= "FALSE"),
         inequality = abs(8 - 2*y)/8.0,
         zero_to_worst_off = (y %in% c(0,8)),
         university = (education %in% c("Universitet/hoyskole I", "Universitet/hoyskole II")),
         high_income = (indincome %in% c("1.000.000 kroner eller mer", 
                                         "800.000 - 999.999 kroner",
                                         "700-000 - 799.999 kroner",
                                         "600.000 - 699.999 kroner",
                                         "500.000 - 599.999 kroner")),  # Median is within 400-499 group.
         female = (gender=="Kvinne"),
         choice = (treatmentgroup %in% c("Forced Choice", "Nominal Choice")),
         age_h = (age > median(age)),
         crt_h = (crt %in% c(2,3)),
         understanding2n = as.numeric(gsub("[^0-9]","", understanding2))) %>%
  filter(comp==1)
```


# Descriptive figures

## Histogram of transfers to the unlucky
First out is a histogram of the transfer to the unlucky participant. I make it for each of the 
three main treatments, with and without work. The "FALSE" means there is no work. 
```{r}
df_k %>% filter(org_weakp==TRUE) %>% 
  ggplot(aes(x=y, y=1* (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_histogram() + facet_grid(work~treatmentgroup) + theme_bw() + ylab("Fraction") + 
  xlab("Transfer from Lucky to Unlucky")
ggsave("graphs/histograms_kantar.pdf")
```
### The share that equalizes
```{r}
df_equal <- df_k %>% mutate(equal = (y==4)) 
df_equal %>% 
  group_by(treatment) %>% 
  summarize(share_equal=mean(equal))
```
```{r}
ce <- df_equal %>%
  group_by(treatment) %>% summarize( yc= sum(y==4), n=n())
prop.test(ce$yc[ce$treatment %in% c("Base (w)", "Nominal Choice (w)") ], 
          ce$n[ce$treatment %in% c("Base (w)", "Nominal Choice (w)") ])
prop.test(ce$yc[ce$treatment %in% c("Base (w)", "Forced Choice (w)") ], 
          ce$n[ce$treatment %in% c("Base (w)", "Forced Choice (w)") ])


```
### The share that gives nothing to unlucky
```{r}
df_0  <- df_k %>% mutate(nothing = (y==0)) 
df_0 %>% 
  group_by(treatment) %>% 
  summarize(share_equal=mean(nothing))
```

```{r}
c0 <- df_0 %>%
  group_by(treatment) %>% summarize( y0= sum(y==0), n=n())
prop.test(c0$y0[c0$treatment %in% c("Base (w)", "Nominal Choice (w)") ], 
          c0$n[c0$treatment %in% c("Base (w)", "Nominal Choice (w)") ])
prop.test(c0$y0[c0$treatment %in% c("Base (w)", "Forced Choice (w)") ], 
          c0$n[c0$treatment %in% c("Base (w)", "Forced Choice (w)") ])
```




## Mean inequality
The next descriptive figure is a bargraph showing the amount of inequality
by treatment and work status.

```{r}
df_mean_ineq_nothing_kantar <- df_k %>% filter(org_weakp==TRUE) %>%
  dplyr::select(treatmentgroup, work, inequality, zero_to_worst_off) %>%
  gather(inequality, zero_to_worst_off, key="outcome", value="y") %>%
  group_by(treatmentgroup, work, outcome) %>%
  summarize(mean_y = mean(y, na.rm=TRUE), se_y = sd(y, na.rm=TRUE)/sqrt(n())) %>%
  mutate(outcome = fct_recode(outcome, 
                              "Inequality" = "inequality",
                              "Nothing to worse off" = "zero_to_worst_off"))
df_mean_ineq_nothing_kantar
df_mean_ineq_nothing_kantar %>%
ggplot(aes(x=treatmentgroup, y=mean_y)) + geom_bar(stat="identity", width=0.7) +
  geom_errorbar(aes(ymax=mean_y+se_y, ymin=mean_y - se_y), width=0.2) + 
  facet_grid(work ~ outcome) + xlab("") + ylab("Mean +/- s.e.m.") +
  theme_bw()
ggsave("graphs/mean_ineq_nothing_kantar.pdf")
```


# Robustness for the "forced" alternative
We did two variations of the "Forced Choice" treatment. One "strong" in which the alternative to the
lottery was 0 cent with certainty, and one in which they actually had to pay 0.25 
to avoid the lottery
(I call it very-strong). Both these variants were with work. 
To look at the effect of this, I graph the level of inequality of the three
forced choice treatments (with work) with the comparison to the base treatment. 

```{r}
df_k %>% filter(treatment %in% c("Base (w)", 
                                 "Forced Choice (w)", 
                                 "Forced Choice strong",
                                 "Forced Choice very strong")) %>%
  dplyr::select(treatment, inequality, zero_to_worst_off) %>%
  gather(inequality, zero_to_worst_off, key="outcome", value="y") %>%
  group_by(treatment, outcome) %>%
  summarize(mean_y = mean(y, na.rm=TRUE), se_y = sd(y, na.rm=TRUE)/sqrt(n())) %>%
  mutate(outcome = fct_recode(outcome, 
                              "Inequality" = "inequality",
                              "Nothing to worse off" = "zero_to_worst_off")) %>%
  ggplot(aes(x=treatment, y=mean_y)) + geom_bar(stat="identity", width=0.7) +
    geom_errorbar(aes(ymax=mean_y+se_y, ymin=mean_y - se_y), width=0.2) + 
    facet_wrap(~ outcome) + xlab("") + ylab("Mean +/- s.e.m.") +
    theme_bw() + scale_x_discrete(labels=c("Base (w)",
                                           "Forced\nChoice (w)", 
                                           "Forced\nChoice\nstrong",
                                           "Forced\nChoice\nvery strong"))
ggsave("graphs/mean_ineq_nothing_robust_kantar.pdf")

```
Are the differences between the forced treatments significant? First a test
of mean implemented inequality being the same in all forced (work) treatments:
```{r}
df_k %>% filter(treatment %in% c("Forced Choice (w)", 
                                 "Forced Choice strong",
                                 "Forced Choice very strong")) %>%
  oneway.test( inequality ~ treatment, data=.)
```

Increases in implemented inequality compared to base treatment (for the forced choice
variants).
```{r}
df_k %>% filter(treatment %in% c("Base (w)", 
                                 "Forced Choice strong")) %>%
  t.test( inequality ~ treatment, data=.)
df_k %>% filter(treatment %in% c("Base (w)", 
                                 "Forced Choice very strong")) %>%
  t.test( inequality ~ treatment, data=.)

```



Now, the same test for the proportion implementing the nothing to the 
worst off:
```{r}
uz <- df_k %>% filter(treatment %in% c("Forced Choice (w)", 
                                 "Forced Choice strong",
                                 "Forced Choice very strong")) %>% 
  group_by(treatment, zero_to_worst_off) %>% 
  summarize(n=n()) %>% 
  spread(key=zero_to_worst_off, value=n) %>% 
  ungroup() %>%
  dplyr::select( -treatment) 
prop.test(as.matrix(uz))
```



# Main regression tables


## Work and treatments
In the following, we want to collapse the work and no-work treatments,
so it is a question of interest whether there are interaction effects between
the work requirement and treatments. 
```{r}
dfmain <- df_k %>% filter(org_weakp==TRUE)

w1 <- dfmain %>% lm(inequality ~ treatmentgroup*workp , data=.)
w2 <- dfmain %>% lm(inequality ~ treatmentgroup*workp + leftp + female + age_h + crt_h +
                             university + high_income, data=.)
w3 <- dfmain %>% lm(inequality ~ treatmentgroup + workp + leftp + female + age_h + crt_h +
                             university + high_income, data=.)
w4 <- dfmain %>% lm(zero_to_worst_off ~ treatmentgroup*workp , data=.)
w5 <- dfmain %>% lm(zero_to_worst_off ~ treatmentgroup*workp + leftp + female + age_h + crt_h +
                             university + high_income, data=.)
w6 <- dfmain %>% lm(zero_to_worst_off ~ treatmentgroup + workp + leftp + female + age_h + crt_h +
                             university + high_income, data=.)
```

We want to test the joint significance of the interactions
```{r}
w1t <- glht(w1, linfct= c("`treatmentgroupForced Choice:workpTRUE` = 0",
                          "`treatmentgroupNominal Choice:workpTRUE` = 0"),
             vcov = cluster.vcov(w1, cluster=1:nrow(dfmain)))
w2t <- glht(w2, linfct= c("`treatmentgroupForced Choice:workpTRUE` = 0",
                          "`treatmentgroupNominal Choice:workpTRUE` = 0"),
             vcov = cluster.vcov(w2, cluster=1:nrow(dfmain)))
w4t <- glht(w4, linfct= c("`treatmentgroupForced Choice:workpTRUE` = 0",
                          "`treatmentgroupNominal Choice:workpTRUE` = 0"),
             vcov = cluster.vcov(w4, cluster=1:nrow(dfmain)))
w5t <- glht(w5, linfct= c("`treatmentgroupForced Choice:workpTRUE` = 0",
                          "`treatmentgroupNominal Choice:workpTRUE` = 0"),
             vcov = cluster.vcov(w5, cluster=1:nrow(dfmain)))

wrow <- c("Joint p-value on work-interactions:", 
          sprintf("%4.3f", summary(w1t)$test$pvalue[1]),
          sprintf("%4.3f", summary(w2t)$test$pvalue[1]), "",
          sprintf("%4.3f", summary(w4t)$test$pvalue[1]),
          sprintf("%4.3f", summary(w5t)$test$pvalue[1]), "")
```

Now for table output:
```{r}
stargazer(w1, w2, w3, w4, w5, w6, 
          se = list(sqrt(diag(cluster.vcov(w1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w3, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w4, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w5, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w6, cluster=1:nrow(dfmain))))),
        add.lines=list(wrow),
        type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        order=c("treatmentgroup*", "workp"),
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp", header=FALSE)
```
From this we conclude that we can pool the work/no-work treatments, and 
simplify with only a dummy for work condition as a level shifter.

Writing the results also to a latex file.

Now for table output:
```{r include=FALSE}
stargazer(w1, w2, w3, w4, w5, w6, 
          se = list(sqrt(diag(cluster.vcov(w1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w3, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w4, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w5, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(w6, cluster=1:nrow(dfmain))))),
        add.lines=list(wrow),
        type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        order=c("treatmentgroup*", "workp"),
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
        out = "tables/work_interactions.tex", header=FALSE)
```




## The role of choice
The first regression table just regress inequality (and zero to the worst off) on treatment indicators and demographics (Table 1 in submitted version). 
Given the graphs we have created, and the previous regression table,
we want the tables to have dummies for"work" condition.



```{r}

t1ineq_1 <-  dfmain %>% lm(inequality ~ treatmentgroup + workp  , data = . )
t1ineq_2 <-  dfmain %>% lm(inequality ~ treatmentgroup + workp +
                             leftp + female + age_h + crt_h, data=.)
t1ineq_3 <-  dfmain %>% lm(inequality ~ treatmentgroup + workp +
                             leftp + female + age_h + crt_h +
                             university + high_income, data=.)

t1noth_1 <-  dfmain %>% lm( zero_to_worst_off ~ treatmentgroup  + workp, data = . )
t1noth_2  <- dfmain %>% lm( zero_to_worst_off ~ treatmentgroup + workp +
                              leftp + female + age_h + crt_h, data=.)
t1noth_3  <- dfmain %>% lm( zero_to_worst_off ~ treatmentgroup + workp +
                              leftp + female + age_h + crt_h +
                              university + high_income, data=.)
```
Now, outputting these regressions to a table.
```{r}
stargazer(t1ineq_1, t1ineq_2, t1ineq_3, t1noth_1, t1noth_2, t1noth_3,
          se = list(sqrt(diag(cluster.vcov(t1ineq_1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1ineq_2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1ineq_3, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1noth_1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1noth_2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1noth_3, cluster=1:nrow(dfmain))))),
         type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp", header=FALSE)
```

And to disk:
```{r include=FALSE}
stargazer(t1ineq_1, t1ineq_2, t1ineq_3, t1noth_1, t1noth_2, t1noth_3,
          se = list(sqrt(diag(cluster.vcov(t1ineq_1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1ineq_2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1ineq_3, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1noth_1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1noth_2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(t1noth_3, cluster=1:nrow(dfmain))))),
         style="aer", df=FALSE, keep.stat=c("rsq","n"), p.auto=TRUE,
         star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
         out = "tables/main_online.tex", header=FALSE)
```

### What if we include also the variant forced choice alternatives?
Now, I repeate the above analysis but without the restriction to the 
6 main treatments.


```{r}
t18ineq_1 <-  df_k %>% lm(inequality ~ treatmentgroup8 + workp  , data = . )
t18ineq_2 <-  df_k %>% lm(inequality ~ treatmentgroup8 + workp +
                             leftp + female + age_h + crt_h, data=.)
t18ineq_3 <-  df_k %>% lm(inequality ~ treatmentgroup8 + workp +
                             leftp + female + age_h + crt_h +
                             university + high_income, data=.)

t18noth_1 <-  df_k %>% lm( zero_to_worst_off ~ treatmentgroup8  + workp, data = . )
t18noth_2  <- df_k %>% lm( zero_to_worst_off ~ treatmentgroup8 + workp +
                              leftp + female + age_h + crt_h, data=.)
t18noth_3  <- df_k %>% lm( zero_to_worst_off ~ treatmentgroup8 + workp +
                              leftp + female + age_h + crt_h +
                              university + high_income, data=.)
```
Now, outputting these regressions to a table.
```{r}
stargazer(t18ineq_1, t18ineq_2, t18ineq_3, t18noth_1, t18noth_2, t18noth_3,
          se = list(sqrt(diag(cluster.vcov(t18ineq_1, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18ineq_2, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18ineq_3, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18noth_1, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18noth_2, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18noth_3, cluster=1:nrow(df_k))))),
         type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp", header=FALSE)
```
Silently to file on disk.
```{r include=FALSE}
stargazer(t18ineq_1, t18ineq_2, t18ineq_3, t18noth_1, t18noth_2, t18noth_3,
         se = list(sqrt(diag(cluster.vcov(t18ineq_1, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18ineq_2, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18ineq_3, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18noth_1, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18noth_2, cluster=1:nrow(df_k)))),
                    sqrt(diag(cluster.vcov(t18noth_3, cluster=1:nrow(df_k))))),
         style="aer", df=FALSE, keep.stat=c("rsq","n"), p.auto=TRUE,
         star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
         out = "tables/main8_online.tex", header=FALSE)
```

## Heterogeneity in effects
In the new heterogeneity table, we treat the background variables symmetrically, so that we don't 
single out "political"" as being of primary importance.

### Heterogeneity in effects on inequality
```{r}
h1_1 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income, 
                      data=. )
h1_2 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp, data=. )
h1_3 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*female , data=. )
h1_4 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*age_h, data=. )
h1_5 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*crt_h, data=. )
h1_6 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*university, data=. )
h1_7 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*high_income, data=. )
h1_8 <- dfmain %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp + choice*female + choice*age_h + choice*crt_h + choice*university + 
                        choice*high_income, data=. )
```

Want to include linear combinations for the columns 2-7:
```{r}
ch2 <- glht(h1_2, linfct="choiceTRUE + choiceTRUE:leftpTRUE = 0", 
             vcov = cluster.vcov(h1_2, cluster=1:nrow(dfmain)))
ch3 <- glht(h1_3, linfct="choiceTRUE + choiceTRUE:femaleTRUE = 0", 
             vcov = cluster.vcov(h1_3, cluster=1:nrow(dfmain)))
ch4 <- glht(h1_4, linfct="choiceTRUE + choiceTRUE:age_hTRUE = 0", 
             vcov = cluster.vcov(h1_4, cluster=1:nrow(dfmain)))
ch5 <- glht(h1_5, linfct="choiceTRUE + choiceTRUE:crt_hTRUE = 0", 
             vcov = cluster.vcov(h1_5, cluster=1:nrow(dfmain)))
ch6 <- glht(h1_6, linfct="choiceTRUE + choiceTRUE:universityTRUE = 0", 
             vcov = cluster.vcov(h1_6, cluster=1:nrow(dfmain)))
ch7 <- glht(h1_7, linfct="choiceTRUE + choiceTRUE:high_incomeTRUE = 0", 
             vcov = cluster.vcov(h1_7, cluster=1:nrow(dfmain)))
sh1 <- c("Linear combination"," ", 
        sprintf("%4.3f", summary(ch2)$test$coefficients[1]),
        sprintf("%4.3f", summary(ch3)$test$coefficients[1]),
        sprintf("%4.3f", summary(ch4)$test$coefficients[1]),
        sprintf("%4.3f", summary(ch5)$test$coefficients[1]),
        sprintf("%4.3f", summary(ch6)$test$coefficients[1]),
        sprintf("%4.3f", summary(ch7)$test$coefficients[1]),
        "")
sh2 <- c("","",
        sprintf("(%4.3f)", summary(ch2)$test$sigma[1]),
        sprintf("(%4.3f)", summary(ch3)$test$sigma[1]),
        sprintf("(%4.3f)", summary(ch4)$test$sigma[1]),
        sprintf("(%4.3f)", summary(ch5)$test$sigma[1]),
        sprintf("(%4.3f)", summary(ch6)$test$sigma[1]),
        sprintf("(%4.3f)", summary(ch7)$test$sigma[1]),
        "")
sh3 <- c("", "",
        sprintf("p=%4.3f", summary(ch2)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(ch3)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(ch4)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(ch5)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(ch6)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(ch7)$test$pvalues[1]),
        "")
```


```{r}
stargazer( h1_1, h1_2, h1_3, h1_4, h1_5, h1_6, h1_7, h1_8,
           se = list( sqrt(diag(cluster.vcov(h1_1, cluster=1:length(h1_1$residuals)))),
                      sqrt(diag(cluster.vcov(h1_2, cluster=1:length(h1_2$residuals)))),
                      sqrt(diag(cluster.vcov(h1_3, cluster=1:length(h1_3$residuals)))),
                      sqrt(diag(cluster.vcov(h1_4, cluster=1:length(h1_4$residuals)))),
                      sqrt(diag(cluster.vcov(h1_5, cluster=1:length(h1_5$residuals)))),
                      sqrt(diag(cluster.vcov(h1_6, cluster=1:length(h1_6$residuals)))),
                      sqrt(diag(cluster.vcov(h1_7, cluster=1:length(h1_7$residuals)))),
                      sqrt(diag(cluster.vcov(h1_8, cluster=1:length(h1_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(sh1,sh2,sh3), 
        type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp")
```
Now to latex table on file
```{r include=FALSE}
stargazer( h1_1, h1_2, h1_3, h1_4, h1_5, h1_6, h1_7, h1_8,
           se = list( sqrt(diag(cluster.vcov(h1_1, cluster=1:length(h1_1$residuals)))),
                      sqrt(diag(cluster.vcov(h1_2, cluster=1:length(h1_2$residuals)))),
                      sqrt(diag(cluster.vcov(h1_3, cluster=1:length(h1_3$residuals)))),
                      sqrt(diag(cluster.vcov(h1_4, cluster=1:length(h1_4$residuals)))),
                      sqrt(diag(cluster.vcov(h1_5, cluster=1:length(h1_5$residuals)))),
                      sqrt(diag(cluster.vcov(h1_6, cluster=1:length(h1_6$residuals)))),
                      sqrt(diag(cluster.vcov(h1_7, cluster=1:length(h1_7$residuals)))),
                      sqrt(diag(cluster.vcov(h1_8, cluster=1:length(h1_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(sh1,sh2), 
        type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
        out="tables/heterogeneity1_representative.tex", header=FALSE )
```


### Restricting heterogeneity table to Nominal Choice
For the appendix, we want to show heterogeneity with respect to each of the types of 
choice separately. First, restricting to nominal choice.
```{r}
dfmain_nc <- dfmain %>% filter(treatmentgroup != "Forced Choice")
```
The regression tables are the same on this more restricted sample.
```{r}
hnc1_1 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income, 
                      data=. )
hnc1_2 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp, data=. )
hnc1_3 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*female , data=. )
hnc1_4 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*age_h, data=. )
hnc1_5 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*crt_h, data=. )
hnc1_6 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*university, data=. )
hnc1_7 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*high_income, data=. )
hnc1_8 <- dfmain_nc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp + choice*female + choice*age_h + choice*crt_h + choice*university + 
                        choice*high_income, data=. )
```

Want to include linear combinations for the columns 2-7:
```{r}
nch2 <- glht(hnc1_2, linfct="choiceTRUE + choiceTRUE:leftpTRUE = 0", 
             vcov = cluster.vcov(hnc1_2, cluster=1:nrow(dfmain_nc)))
nch3 <- glht(hnc1_3, linfct="choiceTRUE + choiceTRUE:femaleTRUE = 0", 
             vcov = cluster.vcov(hnc1_3, cluster=1:nrow(dfmain_nc)))
nch4 <- glht(hnc1_4, linfct="choiceTRUE + choiceTRUE:age_hTRUE = 0", 
             vcov = cluster.vcov(hnc1_4, cluster=1:nrow(dfmain_nc)))
nch5 <- glht(hnc1_5, linfct="choiceTRUE + choiceTRUE:crt_hTRUE = 0", 
             vcov = cluster.vcov(hnc1_5, cluster=1:nrow(dfmain_nc)))
nch6 <- glht(hnc1_6, linfct="choiceTRUE + choiceTRUE:universityTRUE = 0", 
             vcov = cluster.vcov(hnc1_6, cluster=1:nrow(dfmain_nc)))
nch7 <- glht(hnc1_7, linfct="choiceTRUE + choiceTRUE:high_incomeTRUE = 0", 
             vcov = cluster.vcov(hnc1_7, cluster=1:nrow(dfmain_nc)))
nsh1 <- c("Linear combination"," ", 
        sprintf("%4.3f", summary(nch2)$test$coefficients[1]),
        sprintf("%4.3f", summary(nch3)$test$coefficients[1]),
        sprintf("%4.3f", summary(nch4)$test$coefficients[1]),
        sprintf("%4.3f", summary(nch5)$test$coefficients[1]),
        sprintf("%4.3f", summary(nch6)$test$coefficients[1]),
        sprintf("%4.3f", summary(nch7)$test$coefficients[1]),
        "")
nsh2 <- c("","",
        sprintf("(%4.3f)", summary(nch2)$test$sigma[1]),
        sprintf("(%4.3f)", summary(nch3)$test$sigma[1]),
        sprintf("(%4.3f)", summary(nch4)$test$sigma[1]),
        sprintf("(%4.3f)", summary(nch5)$test$sigma[1]),
        sprintf("(%4.3f)", summary(nch6)$test$sigma[1]),
        sprintf("(%4.3f)", summary(nch7)$test$sigma[1]),
        "")
nsh3 <- c("", "",
        sprintf("p=%4.3f", summary(nch2)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(nch3)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(nch4)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(nch5)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(nch6)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(nch7)$test$pvalues[1]),
        "")
```


```{r}
stargazer( hnc1_1, hnc1_2, hnc1_3, hnc1_4, hnc1_5, hnc1_6, hnc1_7, hnc1_8,
           se = list( sqrt(diag(cluster.vcov(hnc1_1, cluster=1:length(hnc1_1$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_2, cluster=1:length(hnc1_2$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_3, cluster=1:length(hnc1_3$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_4, cluster=1:length(hnc1_4$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_5, cluster=1:length(hnc1_5$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_6, cluster=1:length(hnc1_6$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_7, cluster=1:length(hnc1_7$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_8, cluster=1:length(hnc1_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(nsh1,nsh2,nsh3), 
        type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp")
```
Now to latex table on file
```{r include=FALSE}
stargazer( hnc1_1, hnc1_2, hnc1_3, hnc1_4, hnc1_5, hnc1_6, hnc1_7, hnc1_8,
           se = list( sqrt(diag(cluster.vcov(hnc1_1, cluster=1:length(hnc1_1$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_2, cluster=1:length(hnc1_2$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_3, cluster=1:length(hnc1_3$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_4, cluster=1:length(hnc1_4$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_5, cluster=1:length(hnc1_5$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_6, cluster=1:length(hnc1_6$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_7, cluster=1:length(hnc1_7$residuals)))),
                      sqrt(diag(cluster.vcov(hnc1_8, cluster=1:length(hnc1_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(nsh1,nsh2), 
        type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
        out="tables/heterogeneity1_representative_NC.tex", header=FALSE )
```

### Restricting heterogeneity table to Forced Choice
For the appendix, we want to show heterogeneity with respect to each of the types of 
choice separately. Now, restricting to forced choice.


```{r}
dfmain_fc <- dfmain %>% filter(treatmentgroup != "Nominal Choice")
```
The regression tables are the same on this more restricted sample.
```{r}
hfc1_1 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income, 
                      data=. )
hfc1_2 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp, data=. )
hfc1_3 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*female , data=. )
hfc1_4 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*age_h, data=. )
hfc1_5 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*crt_h, data=. )
hfc1_6 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*university, data=. )
hfc1_7 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*high_income, data=. )
hfc1_8 <- dfmain_fc %>% lm(inequality ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp + choice*female + choice*age_h + choice*crt_h + choice*university + 
                        choice*high_income, data=. )
```

Want to include linear combinations for the columns 2-7:
```{r}
fch2 <- glht(hfc1_2, linfct="choiceTRUE + choiceTRUE:leftpTRUE = 0", 
             vcov = cluster.vcov(hfc1_2, cluster=1:nrow(dfmain_fc)))
fch3 <- glht(hfc1_3, linfct="choiceTRUE + choiceTRUE:femaleTRUE = 0", 
             vcov = cluster.vcov(hfc1_3, cluster=1:nrow(dfmain_fc)))
fch4 <- glht(hfc1_4, linfct="choiceTRUE + choiceTRUE:age_hTRUE = 0", 
             vcov = cluster.vcov(hfc1_4, cluster=1:nrow(dfmain_fc)))
fch5 <- glht(hfc1_5, linfct="choiceTRUE + choiceTRUE:crt_hTRUE = 0", 
             vcov = cluster.vcov(hfc1_5, cluster=1:nrow(dfmain_fc)))
fch6 <- glht(hfc1_6, linfct="choiceTRUE + choiceTRUE:universityTRUE = 0", 
             vcov = cluster.vcov(hfc1_6, cluster=1:nrow(dfmain_fc)))
fch7 <- glht(hfc1_7, linfct="choiceTRUE + choiceTRUE:high_incomeTRUE = 0", 
             vcov = cluster.vcov(hfc1_7, cluster=1:nrow(dfmain_fc)))
fsh1 <- c("Linear combination"," ", 
        sprintf("%4.3f", summary(fch2)$test$coefficients[1]),
        sprintf("%4.3f", summary(fch3)$test$coefficients[1]),
        sprintf("%4.3f", summary(fch4)$test$coefficients[1]),
        sprintf("%4.3f", summary(fch5)$test$coefficients[1]),
        sprintf("%4.3f", summary(fch6)$test$coefficients[1]),
        sprintf("%4.3f", summary(fch7)$test$coefficients[1]),
        "")
fsh2 <- c("","",
        sprintf("(%4.3f)", summary(fch2)$test$sigma[1]),
        sprintf("(%4.3f)", summary(fch3)$test$sigma[1]),
        sprintf("(%4.3f)", summary(fch4)$test$sigma[1]),
        sprintf("(%4.3f)", summary(fch5)$test$sigma[1]),
        sprintf("(%4.3f)", summary(fch6)$test$sigma[1]),
        sprintf("(%4.3f)", summary(fch7)$test$sigma[1]),
        "")
fsh3 <- c("", "",
        sprintf("p=%4.3f", summary(fch2)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(fch3)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(fch4)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(fch5)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(fch6)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(fch7)$test$pvalues[1]),
        "")
```


```{r}
stargazer( hfc1_1, hfc1_2, hfc1_3, hfc1_4, hfc1_5, hfc1_6, hfc1_7, hfc1_8,
           se = list( sqrt(diag(cluster.vcov(hfc1_1, cluster=1:length(hfc1_1$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_2, cluster=1:length(hfc1_2$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_3, cluster=1:length(hfc1_3$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_4, cluster=1:length(hfc1_4$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_5, cluster=1:length(hfc1_5$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_6, cluster=1:length(hfc1_6$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_7, cluster=1:length(hfc1_7$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_8, cluster=1:length(hfc1_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(fsh1,fsh2,fsh3), 
        type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp")
```

Now to latex table on file
```{r include=FALSE}
stargazer( hfc1_1, hfc1_2, hfc1_3, hfc1_4, hfc1_5, hfc1_6, hfc1_7, hfc1_8,
           se = list( sqrt(diag(cluster.vcov(hfc1_1, cluster=1:length(hfc1_1$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_2, cluster=1:length(hfc1_2$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_3, cluster=1:length(hfc1_3$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_4, cluster=1:length(hfc1_4$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_5, cluster=1:length(hfc1_5$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_6, cluster=1:length(hfc1_6$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_7, cluster=1:length(hfc1_7$residuals)))),
                      sqrt(diag(cluster.vcov(hfc1_8, cluster=1:length(hfc1_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(fsh1,fsh2), 
        type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
        out="tables/heterogeneity1_representative_FC.tex", header=FALSE )
```


### Heterogeneity in effects on zero to worst off
```{r}
h2_1 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income, 
                      data=. )
h2_2 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp, data=. )
h2_3 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*female , data=. )
h2_4 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*age_h, data=. )
h2_5 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*crt_h, data=. )
h2_6 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*university, data=. )
h2_7 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*high_income, data=. )
h2_8 <- dfmain %>% lm(zero_to_worst_off ~ choice + leftp + workp + crt_h + female + age_h + university + high_income +
                        choice*leftp + choice*female + choice*age_h + choice*crt_h + choice*university + 
                        choice*high_income, data=. )
```
Want to include linear combinations for the columns 2-7:
```{r}
dh2 <- glht(h2_2, linfct="choiceTRUE + choiceTRUE:leftpTRUE = 0", 
             vcov = cluster.vcov(h2_2, cluster=1:nrow(dfmain)))
dh3 <- glht(h2_3, linfct="choiceTRUE + choiceTRUE:femaleTRUE = 0", 
             vcov = cluster.vcov(h2_3, cluster=1:nrow(dfmain)))
dh4 <- glht(h2_4, linfct="choiceTRUE + choiceTRUE:age_hTRUE = 0", 
             vcov = cluster.vcov(h2_4, cluster=1:nrow(dfmain)))
dh5 <- glht(h2_5, linfct="choiceTRUE + choiceTRUE:crt_hTRUE = 0", 
             vcov = cluster.vcov(h2_5, cluster=1:nrow(dfmain)))
dh6 <- glht(h2_6, linfct="choiceTRUE + choiceTRUE:universityTRUE = 0", 
             vcov = cluster.vcov(h2_6, cluster=1:nrow(dfmain)))
dh7 <- glht(h2_7, linfct="choiceTRUE + choiceTRUE:high_incomeTRUE = 0", 
             vcov = cluster.vcov(h2_7, cluster=1:nrow(dfmain)))
rh1 <- c("Linear combination"," ", 
        sprintf("%4.3f", summary(dh2)$test$coefficients[1]),
        sprintf("%4.3f", summary(dh3)$test$coefficients[1]),
        sprintf("%4.3f", summary(dh4)$test$coefficients[1]),
        sprintf("%4.3f", summary(dh5)$test$coefficients[1]),
        sprintf("%4.3f", summary(dh6)$test$coefficients[1]),
        sprintf("%4.3f", summary(dh7)$test$coefficients[1]),
        "")
rh2 <- c("","",
        sprintf("(%4.3f)", summary(dh2)$test$sigma[1]),
        sprintf("(%4.3f)", summary(dh3)$test$sigma[1]),
        sprintf("(%4.3f)", summary(dh4)$test$sigma[1]),
        sprintf("(%4.3f)", summary(dh5)$test$sigma[1]),
        sprintf("(%4.3f)", summary(dh6)$test$sigma[1]),
        sprintf("(%4.3f)", summary(dh7)$test$sigma[1]),
        "")
rh3 <- c("", "",
        sprintf("p=%4.3f", summary(dh2)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(dh3)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(dh4)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(dh5)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(dh6)$test$pvalues[1]),
        sprintf("p=%4.3f", summary(dh7)$test$pvalues[1]),
        "")
```

Now for table output with p-values:
```{r}
stargazer( h2_1, h2_2, h2_3, h2_4, h2_5, h2_6, h2_7, h2_8,
           se = list( sqrt(diag(cluster.vcov(h2_1, cluster=1:length(h2_1$residuals)))),
                      sqrt(diag(cluster.vcov(h2_2, cluster=1:length(h2_2$residuals)))),
                      sqrt(diag(cluster.vcov(h2_3, cluster=1:length(h2_3$residuals)))),
                      sqrt(diag(cluster.vcov(h2_4, cluster=1:length(h2_4$residuals)))),
                      sqrt(diag(cluster.vcov(h2_5, cluster=1:length(h2_5$residuals)))),
                      sqrt(diag(cluster.vcov(h2_6, cluster=1:length(h2_6$residuals)))),
                      sqrt(diag(cluster.vcov(h2_7, cluster=1:length(h2_7$residuals)))),
                      sqrt(diag(cluster.vcov(h2_8, cluster=1:length(h2_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(rh1,rh2,rh3), 
        type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        p.auto=TRUE,
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp")
```

Want to output also to latex table.

```{r include=FALSE}
stargazer( h2_1, h2_2, h2_3, h2_4, h2_5, h2_6, h2_7, h2_8,
           se = list( sqrt(diag(cluster.vcov(h2_1, cluster=1:length(h2_1$residuals)))),
                      sqrt(diag(cluster.vcov(h2_2, cluster=1:length(h2_2$residuals)))),
                      sqrt(diag(cluster.vcov(h2_3, cluster=1:length(h2_3$residuals)))),
                      sqrt(diag(cluster.vcov(h2_4, cluster=1:length(h2_4$residuals)))),
                      sqrt(diag(cluster.vcov(h2_5, cluster=1:length(h2_5$residuals)))),
                      sqrt(diag(cluster.vcov(h2_6, cluster=1:length(h2_6$residuals)))),
                      sqrt(diag(cluster.vcov(h2_7, cluster=1:length(h2_7$residuals)))),
                      sqrt(diag(cluster.vcov(h2_8, cluster=1:length(h2_8$residuals))))),
        order=c("choice","choiceTRUE:leftp","choiceTRUE:female", "choiceTRUE:age_h",
                "choiceTRUE:crt_h", "choiceTRUE:universityTRUE", "choiceTRUE:high_incomeTRUE"),
        add.lines=list(rh1,rh2), 
        type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"),
        star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
        out="tables/heterogeneity2_representative.tex", header=FALSE )
```


## Absolutely no effect on any party?
In the lab experiment, we found a strong interaction between political affiliation
and treatment.  Are there really no interactions of choice and political 
preference in the representative sample? Let us try to run the treatment regressions party-by-party:

### Treatment effects by political party
On inequality:
```{r}
rAp <-dfmain %>% filter(stortingsvalg=="Ap") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rFrp <-dfmain %>% filter(stortingsvalg=="Frp") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rH <-dfmain %>% filter(stortingsvalg=="H") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rKrF <-dfmain %>% filter(stortingsvalg=="KrF") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rMDG <-dfmain %>% filter(stortingsvalg=="MDG") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rR <-dfmain %>% filter(stortingsvalg=="R") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rSp <-dfmain %>% filter(stortingsvalg=="Sp") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rSV <-dfmain %>% filter(stortingsvalg=="SV") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)
rV <-dfmain %>% filter(stortingsvalg=="V") %>% 
  lm(inequality~choice + workp + female + age_h + crt_h + university + high_income, data=.)

stargazer( rR, rSV, rMDG, rAp, rSp, rKrF, rV, rH, rFrp,
           se = list(sqrt(diag(cluster.vcov(rR, cluster=1:length(rR$residuals)))),
                     sqrt(diag(cluster.vcov(rSV, cluster=1:length(rSV$residuals)))),
                     sqrt(diag(cluster.vcov(rMDG, cluster=1:length(rMDG$residuals)))),
                     sqrt(diag(cluster.vcov(rAp, cluster=1:length(rAp$residuals)))),
                     sqrt(diag(cluster.vcov(rSp, cluster=1:length(rSp$residuals)))),
                     sqrt(diag(cluster.vcov(rKrF, cluster=1:length(rKrF$residuals)))),
                     sqrt(diag(cluster.vcov(rV, cluster=1:length(rV$residuals)))),
                     sqrt(diag(cluster.vcov(rH, cluster=1:length(rH$residuals)))),
                     sqrt(diag(cluster.vcov(rFrp, cluster=1:length(rFrp$residuals))))),
           column.labels=c("R","SV","MDG","Ap","Sp","KrF","V","H","Frp"),
           star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp",
           type="text",  style="aer", df=FALSE, keep.stat=c("rsq","n"))
```

Output to latex (silent):
```{r include=FALSE}
stargazer( rR, rSV, rMDG, rAp, rSp, rKrF, rV, rH, rFrp,
           se = list(sqrt(diag(cluster.vcov(rR, cluster=1:length(rR$residuals)))),
                     sqrt(diag(cluster.vcov(rSV, cluster=1:length(rSV$residuals)))),
                     sqrt(diag(cluster.vcov(rMDG, cluster=1:length(rMDG$residuals)))),
                     sqrt(diag(cluster.vcov(rAp, cluster=1:length(rAp$residuals)))),
                     sqrt(diag(cluster.vcov(rSp, cluster=1:length(rSp$residuals)))),
                     sqrt(diag(cluster.vcov(rKrF, cluster=1:length(rKrF$residuals)))),
                     sqrt(diag(cluster.vcov(rV, cluster=1:length(rV$residuals)))),
                     sqrt(diag(cluster.vcov(rH, cluster=1:length(rH$residuals)))),
                     sqrt(diag(cluster.vcov(rFrp, cluster=1:length(rFrp$residuals))))),
           column.labels=c("R","SV","MDG","Ap","Sp","KrF","V","H","Frp"),
           star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
           type="latex",  style="aer", df=FALSE, keep.stat=c("rsq","n"), out="tables/all_parties.tex", header=FALSE)
```


## Triple interactions 
The editor is interested in the possible triple interaction between political, left, and cognitive reflection.


```{r}
triple1 <- dfmain %>% lm(inequality ~ choice + workp + leftp + crt_h + female + age_h + university + high_income , data=.)
triple2 <- dfmain %>% lm(inequality ~ choice + workp + choice*leftp + leftp + crt_h + female + age_h + university + high_income, data=.)
triple3 <- dfmain %>% lm(inequality ~ choice + workp + choice*crt_h + leftp + crt_h + female + age_h + university + high_income, data=. )
triple4 <- dfmain %>% lm(inequality ~ choice + workp + choice*leftp + choice*crt_h + leftp + crt_h +  female + age_h + 
                           university + high_income, data=. )
triple5 <- dfmain %>% lm(inequality ~ choice + workp + choice*leftp + choice*crt_h + leftp*crt_h + leftp + crt_h +  
                           female + age_h +university + high_income , data=. )
triple6 <- dfmain %>% lm(inequality ~ choice + workp + choice*leftp + choice*crt_h + leftp*crt_h + choice*leftp*crt_h + 
                           leftp + crt_h +  female + age_h +university + high_income, data=. )

stargazer(triple1, triple2, triple3, triple4, triple5, triple6,
          se = list(sqrt(diag(cluster.vcov(triple1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple3, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple4, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple5, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple6, cluster=1:nrow(dfmain))))),
        style="aer", df=FALSE, keep.stat=c("rsq","n"), p.auto=TRUE,
         star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp", type="text")
```

And also to latex (silent).
```{r include=FALSE}
stargazer(triple1, triple2, triple3, triple4, triple5, triple6,
          se = list(sqrt(diag(cluster.vcov(triple1, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple2, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple3, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple4, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple5, cluster=1:nrow(dfmain)))),
                    sqrt(diag(cluster.vcov(triple6, cluster=1:nrow(dfmain))))),
        style="aer", df=FALSE, keep.stat=c("rsq","n"), p.auto=TRUE,
         star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs", type="latex", 
        out="tables/triple_representative.tex", header=FALSE)
```
# Understanding / Mechanisms

We collected information of two types that we can use to get an idea of how participants thought about
the experiment. 
1. We asked those in "nominal choice" whether they believed "Var det like sannsynlig at deltakerne valgte fargen til den ballen som senere ble trukket"
2. We asked all "For du gjorde ditt valg tjente deltaker A 8 USD mens deltaker B tjente 0 USD pa"

## In nominal choice
A clear majority said "yes", but some said I don't know:
```{r}
table(df_k$understanding1)
df_k %>% filter(treatmentgroup=="Nominal Choice") %>%
  ggplot(aes(x=understanding1, y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
  geom_bar(width=0.7) + theme_bw() + 
  labs(title= "Equally likely in nominal choice?",
                                x="", y = "Fraction")
```

Did those who didn't understand distribute any differently than others? 
```{r}
u1 <- df_k %>% filter(treatmentgroup == "Nominal Choice") %>% 
  dplyr::select(understanding1, inequality, zero_to_worst_off) %>%
  gather(inequality, zero_to_worst_off, key="outcome", value="y") %>%
  mutate(understand = fct_recode(understanding1,
                                 "Understand" = "Ja",
                                 "Don't understand" = "Nei",
                                 "Don't understand" = "Vet ikke")) %>%
  group_by(understand, outcome) 
u1 %>% 
  summarize(mean_y = mean(y, na.rm=TRUE), se_y = sd(y, na.rm=TRUE)/sqrt(n())) %>%
  mutate(outcome = fct_recode(outcome,
                              "Inequality" = "inequality", 
                              "Nothing to worse off" = "zero_to_worst_off")) %>%
  ggplot(aes(x=understand, y=mean_y)) + geom_bar(stat="identity", width=0.7) + 
    geom_errorbar(aes(ymax=mean_y+se_y, ymin=mean_y-se_y), width=0.2) + 
  facet_wrap(~outcome, scales="free") +
  xlab("Was the probability of winning equal in Nominal Choice situation?") + 
  ylab("Mean +/- s.e.m.") + theme_bw()
```
Are these differences significant?
```{r}
u1 %>% filter(outcome=="inequality") %>% t.test(y ~ understand, data=.)
u1z <- u1 %>% filter(outcome=="zero_to_worst_off") %>% 
  group_by(understand, y) %>% 
  summarize(n=n()) %>% 
  spread(key=understand, value=n) %>% 
  dplyr::select(-y) 
prop.test(as.matrix(u1z))
```



## Control over earnings before distribution choice
We asked whether the two participants had any control over their own earnings before the DM made their
choices.

```{r}
df_k %>% filter(!is.na(understanding2n)) %>% 
  ggplot(aes(x=understanding2n, y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) + 
  geom_bar(width=0.7) + 
  facet_wrap(~treatment) + theme_bw() + 
  labs(x="Answer from 1-7. (1: no control, ..., 7: full control)", y = "Fraction") +
  scale_x_discrete(limits=c(1,2,3,4,5,6,7))
ggsave("graphs/control_earnings.pdf")
```


What are the exact shares at "no control"?
```{r}
df_k %>% group_by(treatment) %>% 
  summarize(share_no_control = mean( (understanding2n==1), na.rm=TRUE),
                                           n = n())
```
Also by treatmentgroup (excluding "strong" and "very strong"):
```{r}
df_k %>% group_by(treatmentgroup) %>% 
  summarize(share_no_control = mean( (understanding2n==1), na.rm=TRUE),
                                           n = n())
```


### Mediation ...
Can we explain understanding with treatmentgroup? And does understanding
knock out the treatment efects?
```{r}
dfmainu2 <- dfmain %>% filter(!is.na(understanding2n))
ru2_1 <- dfmainu2 %>% lm(understanding2n ~ treatmentgroup + workp + leftp + female + age_h + crt_h +
                           university + high_income , data=.)
ru2_2 <- dfmainu2 %>% lm(inequality ~ treatmentgroup + workp + leftp + female + age_h + crt_h +
                           university + high_income, data=.)
ru2_3 <- dfmainu2 %>% lm(inequality ~ treatmentgroup + understanding2n + workp + leftp + 
                           female + age_h + crt_h + university + high_income, data=.)
ru2_4 <- dfmainu2 %>% lm(inequality ~ treatmentgroup + factor(understanding2n) + workp + 
                           leftp + female + age_h + crt_h + university + high_income, data=.)
ru2_5 <- dfmainu2 %>% lm(zero_to_worst_off ~ treatmentgroup + workp + leftp + 
                           female + age_h + crt_h + university + high_income, data=.)
ru2_6 <- dfmainu2 %>% lm(zero_to_worst_off ~ treatmentgroup + understanding2n + workp + 
                           leftp + female + age_h + crt_h + university + high_income, data=.)
ru2_7 <- dfmainu2 %>% lm(zero_to_worst_off ~ treatmentgroup + factor(understanding2n) + workp +
                           leftp + female + age_h + crt_h + university + high_income,  data=.)

stargazer( ru2_1, ru2_2, ru2_3, ru2_4, ru2_5, ru2_6, ru2_7,
           se = list( sqrt(diag(cluster.vcov(ru2_1, cluster=1:length(ru2_1$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_2, cluster=1:length(ru2_2$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_3, cluster=1:length(ru2_3$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_4, cluster=1:length(ru2_4$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_5, cluster=1:length(ru2_5$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_6, cluster=1:length(ru2_6$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_7, cluster=1:length(ru2_7$residuals))))),
           type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"),
           star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp", header=FALSE)
```

Also to latex (silent):
```{r include=FALSE}
stargazer( ru2_1, ru2_2, ru2_3, ru2_4, ru2_5, ru2_6, ru2_7,
           se = list( sqrt(diag(cluster.vcov(ru2_1, cluster=1:length(ru2_1$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_2, cluster=1:length(ru2_2$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_3, cluster=1:length(ru2_3$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_4, cluster=1:length(ru2_4$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_5, cluster=1:length(ru2_5$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_6, cluster=1:length(ru2_6$residuals)))),
                      sqrt(diag(cluster.vcov(ru2_7, cluster=1:length(ru2_7$residuals))))),
           type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"),
           star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
           out="tables/mediation_online.tex", header=FALSE)
```


We see that treatment does have a sizable effect on understanding, but that the effects
of choice remains strong even when controlling for the level of understanding. This does not
depend on how the understanding is added linearly (as seen by comparing column 3 vs 4, and 6 vs 7).

We see that the total number of observations is lower than in the main regressions. This is because
some respondents chose the "don't know" option, and these don't enter the regressions (or the graph above). 
The proportion that choice the "don't know" option was not much different by treatment:
```{r}
df_k %>% group_by(treatment) %>% summarize(share_dont_know = mean(understanding2=="Vet ikke"))
```


### Restricting to those that were not confused
Can we still find the main treatmentgroup if we exclude all those who are in doubt about
the workers not having control? Let's re-estimate the main table for the representative
sample on the subset of people who are absoluteley sure.

```{r}
df_c <- dfmain %>% filter(understanding2n==1)

cineq_1 <-  df_c %>% lm(inequality ~ treatmentgroup + workp  , data = . )
cineq_2 <-  df_c %>% lm(inequality ~ treatmentgroup + workp +
                             leftp + female + age_h + crt_h, data=.)
cineq_3 <-  df_c %>% lm(inequality ~ treatmentgroup + workp +
                             leftp + female + age_h + crt_h +
                             university + high_income, data=.)

cnoth_1 <-  df_c %>% lm( zero_to_worst_off ~ treatmentgroup  + workp, data = . )
cnoth_2  <- df_c %>% lm( zero_to_worst_off ~ treatmentgroup + workp +
                              leftp + female + age_h + crt_h, data=.)
cnoth_3  <- df_c %>% lm( zero_to_worst_off ~ treatmentgroup + workp +
                              leftp + female + age_h + crt_h +
                              university + high_income, data=.)
```
Now, outputting these regressions to a table.
```{r}
stargazer(cineq_1, cineq_2, cineq_3, cnoth_1, cnoth_2, cnoth_3,
          se = list(sqrt(diag(cluster.vcov(cineq_1, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cineq_2, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cineq_3, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cnoth_1, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cnoth_2, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cnoth_3, cluster=1:nrow(df_c))))),
         type="text", style="aer", df=FALSE, keep.stat=c("rsq","n"), 
         p.auto=TRUE,
         star.char=c("", "",""), notes="", notes.append=FALSE, report="vcsp")
```

Also to latex (silent):
```{r include=FALSE}
stargazer(cineq_1, cineq_2, cineq_3, cnoth_1, cnoth_2, cnoth_3,
          se = list(sqrt(diag(cluster.vcov(cineq_1, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cineq_2, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cineq_3, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cnoth_1, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cnoth_2, cluster=1:nrow(df_c)))),
                    sqrt(diag(cluster.vcov(cnoth_3, cluster=1:nrow(df_c))))),
         type="latex", style="aer", df=FALSE, keep.stat=c("rsq","n"), 
         p.auto=TRUE,
         star.char=c("", "",""), notes="", notes.append=FALSE, report="vcs",
         out="tables/nocontrol_representative.tex", header=FALSE)
```




# Balance table (appendix)
```{r}
dfk_summary <- df_k %>% group_by(treatment) %>% summarize(mean_age = mean(age), se_age = sd(age)/sqrt(n()),
                                                          mean_female = mean(female), se_female=sd(female)/sqrt(n()),
                                                          mean_crt = mean(crt), se_crt = sd(crt)/sqrt(n()),
                                                          mean_left = mean(leftp), se_leftp=sd(leftp)/sqrt(n()),
                                                          n= n())
dfk_totals <- df_k %>% summarize(mean_age = mean(age), se_age = sd(age)/sqrt(n()),
                                 mean_female = mean(female), se_female=sd(female)/sqrt(n()),
                                 mean_crt = mean(crt), se_crt = sd(crt)/sqrt(n()),
                                 mean_left = mean(leftp), se_leftp=sd(leftp)/sqrt(n()),
                                 n= n())
```
Output of balance table
```{r}
dfk_summary %>% knitr::kable(digits=c(3,1,2,2,2,2,2,2,2,0))
dfk_totals %>% knitr::kable(digits=c(1,2,2,2,2,2,2,2,0))
```
# sessionInfo()
```{r}
sessionInfo()
```


