---
title: "Implied risk aversion of safe alternative"
author: "Alexander W. Cappelen, Sebastian Fest, Erik Ø. Sørensen, and Bertil Tungodden"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{risk-aversion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 4.5,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mmbruteluck)
library(rootSolve)
```

Since we implemented the forced choice with a small safe amount as alternative,
participants with sufficient risk aversion might have opted out for this reason.
To quantify the risk aversion needed, consider a CARA utility function,
$$ u(c) = 1 - e^{-\gamma c},$$
where $\gamma$ is the coefficient of absoloute risk aversion.  This
function has the advantage that choices between a set of lotteries is
independent of current wealth, and since wealth is unobserved in the
experiment, this is an advantage. However, the risk aversion is
dependent on the scale of outcomes, so a translation to a common
monetary scale is necessary.

In the online experiment, the main Forced Choice was between 0.25 USD
(safe) and a $\{0,8\}$ uniform lottery in 2017 USD and at US prices
(for the AMT prticipants). The indifference condition between the safe alternati
ve
and the lottery is
$$ 1 - e^{-\gamma 0.25\ } = \frac{1}{2}\left(1 - e^{-\gamma 8.00} \right).$$
```{r}
fun1 <- function(gamma) {
  1 - exp(-gamma * 0.25 ) - (0.5*(1-exp(-gamma* 8.0)))
}
(root1 <- uniroot(fun1, c(1,3)))
```
So this equation has a solution at $\gamma=$ `r root1$root`.

In the lab experiment, the Forced Choice was between 25 NOK (safe) and
a $\{0,800\}$ NOK lottery, in 2012 NOK and Norwegian prices. To
convert into the same reference scale as the online lottery, we take
into account that the 2012 NOK/USD exchange rate was
5.281,[^1] 
  the WDI purchasing power adjustment for Norwegian vs US price level
  puts the Norwegian price level at 1.553 that of the
  US,[^2] 
and the 2012 to 2017 US inflation rate was 1.0714.[^3] 
Taking this into account, the indifference equation is
$$ 1 - e^{-\gamma \frac{25\cdot 1.0714}{5.281\cdot 1.553}} =
\frac{1}{2}\left(1 - e^{-\gamma \frac{800\cdot 1.0714}{5.281\cdot
      1.553}} \right).
$$

```{r}
fun2 <- function(gamma) {
  1 - exp(-gamma * 25*1.0714/(5.281*1.553) ) - (0.5*(1-exp(-gamma * 800*1.0714/(5.281*1.553))))
}
(root2 <- uniroot(fun2, c(0.1,0.3)))
```    
So this equation has a solution at $\gamma=$ `r root2$root`.

In order to evaluate if these are large or small risk aversions, we consider
the paper of Choi et al (2007).[^4] They estimate a distribution of CARA parameters
for a lab population. They report the 95th percentile for the ARA coefficient
to be 0.159.[^5] 
 Considering US inflation factor from 2007 to 2017 of 1.1997,[^6]
we find a 2017 referenced 95th percentile at $\gamma=0.159/1.1997=0.13$. We conclude
that both the critical values we find for the Forced Choice in our experiments
are well above the 95th percentile of estimated absolute risk aversion
in Choi et al (2007).


[^1]: <https://www.norges-bank.no/Statistikk/Valutakurser/>
[^2]: Using the 2012 number from the **PP.NUS.PPC.RF** series 
  from <https://data.worldbank.org/products/wdi>
[^3]: January 2012 to January 2017, <https://www.bls.gov/data/inflation_calculator.htm>
[^4]: Choi, S.; Fisman, R.; Gale, D. & Kariv, S. 
    Consistency and Heterogeneity of Individual Behavior under Uncertainty American Economic Review, 
    2007, 97, 1921-1938
[^5]: In the lower panel of their Table 3.
[^6]: January 2007 to January 2017, <https://www.bls.gov/data/inflation_calculator.htm>

