---
title: "Power analysis for the online experiment"
author: "Alexander W. Cappelen, Sebastian Fest, Erik Ø. Sørensen, and Bertil Tungodden"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{E-power-analysis-online-experiment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Power analysis before the online experiment was based on 
us seeing if we could replicate the large interaction effect between 
"left" political preference and the treatment involving "choice". The
relevant regression coefficient on inequality was -0.192 with a standard
error of 0.074. We wanted more treatment variants in the online
experiment, but wanted to test if this replicated in what corresponds
to the 3-treatment subset that would be most similar to the lab experiment
(base, forced, and nominal choice -- with work). We also wanted sufficient
power even for a more moderate effect size of 0.1. 

To apply the R t-test command, we scale the coefficient to fit into 
a t-test framework. What kind of power would 700 participants per
treatments give us? Test of a regression coefficient against null
is equivalent to a one-sample test in pooled data.

```{r}
SD <- 0.074 * sqrt(422)   # SE and n from lab experiment
power.t.test(n=700*3, delta=0.1, sd=SD, sig.level=0.05, 
             type="one.sample", alternative="one.sided")
```

Even if we were to consider a two-sided test of the null, we would have
sufficient power: 
```{r}
power.t.test(n=700*3, delta=0.1, sd=SD, sig.level=0.05, 
             type="one.sample", alternative="two.sided")
```

