---
title: "4. Risk aversion and forced choice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{risk-aversion}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mmbruteluck)
library(rootSolve)
require("WDI")
```

In the experiment's forced choice condition, partipants choose between a fixed a
mount (25 NOK in lab experiment, 0.25 USD in online experiment), and a lottery (
between 0/800 NOK in lab, 0/8 USD online).
We want to find the risk aversion that makes people indifferent between these
alternatives and compare this to known risk aversions in the literature. 

Since we don't know the level of background wealth, it is convenient to work wit
h
an CARA function, since this has the benefit that risk aversion for a given lott
ery is 
independent of wealth. A disadvantage is that its ARA measure is indexed to the 
value of
a given currency. 

$$ u(c) = 1 - e^{- \gamma c}$$

We want to compare to the numbers in Choi, Syngjoo, Raymond Fisman, Douglas Gale
, and Shachar Kariv. 2007. "Consistency and Heterogeneity of Individual Behavior
 under Uncertainty." American Economic Review, 97 (5): 1921-1938. <https://www.a
eaweb.org/articles?id=10.1257/aer.97.5.1921> We aim
to translate all ARA numbers to the benchmark of the latest data collection (in 
2017), which
was in terms of USD for mostly US participants (Amazon mTurk). 


# Data sources
Exchange rates from <https://www.norges-bank.no/Statistikk/Valutakurser/>
In 2012: 5.821 NOK/USD. 

Consumer prices from <https://www.bls.gov/data/inflation_calculator.htm>
Jan 2007 to Jan 2017: 1.1997.
Jan 2012 to Jan 2017: 1.0714.

# Online sample
For the online sample, the critical equation is, , 
$$ 1 - e^{-\gamma 0.25\ } = \frac{1}{2}\left(1 - e^{-\gamma 8.00} \right).$$
```{r}
labo <- function(gamma) {
  0.5 + 0.5*exp(-gamma * 8.0) - exp(-gamma*(0.25))
}
oroot<-uniroot( labo, c(0.001,10))
```
The rate of absolute risk aversion necessary for choosing the safe alternative
in the 2017 online experiment is **`r oroot$root`** (referenced to 2017 USD and US-prices).

# Lab sample

For the lab sample, the critical equation. translating Norwegian amounts at Norwegian
prices into USD at US 2017 prices is 
$$ 1 - e^{-\gamma \frac{25\cdot 1.0714}{5.281\cdot 1.553}} = 
\frac{1}{2}\left(1 - e^{-\gamma \frac{800\cdot 1.0714}{5.281\cdot 1.553}} \right).$$
We can try to get rootSolve to do solve it for us
```{r}
labf <- function(gamma) {
  0.5 + 0.5*exp(-gamma * 800 * 1.0714 / ( 5.821 * 1.553)) - 
    exp(-gamma * 25 * 1.0714/( 5.821 * 1.553)) 
}
froot <- uniroot( labf, c(0.001,10))
```
The rate of absolute risk aversion necessary for choosing the safe alternative
in the 2012 lab experiment is **`r froot$root`** (referenced to 2017 US dollars and prices). 

# Comparing to estimates from Choi et al (2007). 
In table 3, panel 2, Choi et al report a 95th percentile of 0.159 for the
ARA coefficient. Translating by the CPI factor, we get a 2017 referenced
95th percentile of **`r 0.159/1.1997`**. We conclude that both the
critical values we find for the Forced Choice in our experiments are 
well above the 95th percentile of estimated absolute risk aversion
in Choi et al (2007). 

